\section{Introduction}
\label{sec:introduction}

% Always edit your text without the use of
% word-wrap, like the paragraphs in this section,
% because: 
%
% 1. Hard-breaks make it easier to track changes
%    in version control. 
% 2. It is easier to insert comments explaining
%    some aspect of your writing mid-sentence
% 3. You can break up the structure of your 
%    sentence across multiple lines so that it
%    is easier to edit later. 

% If you are having trouble structuring or phrasing
% your text, try summarising the key point of what
% you want to get across in a leading comment, like
% this:

% This section sets the stage for the paper
This section should clearly explain the problem addressed 
by the paper, and give high level details of your approach
for tackling it, explaining why no other paper already
addresses the exact same problem.

Like the abstract, it should provide a brief summary of 
the results of the paper, with some statistics if possible. 
If you can use some different statistics to the 
abstract, then that helps vary things for the reader.

Right before this section concludes, it should always
feature a list of {\em contributions} that the paper makes.
A contribution is a technical contribution to the 
research literature. What things does your paper show
that no other paper does? Contributions are things 
like your approach/technique. 
One contribution can be the empirical evaluation and
its results. Again, you may wish to highlight some 
key results here, with some numbers. 

The contributions of this paper, therefore, are as follows:

\begin{enumerate}

    \item Contribution 1. Longer description
    (Section where the reader can find this contribution).
    
    \item Contribution 2. Longer description
    (Section where the reader can find this contribution).

\end{enumerate}    

Try to avoid concluding the introduction with a 
``This paper is organized as follows\ldots'' paragraph,
as they are rarely insightful! 
%
However, you may want to include a sentence or two 
leading into the next section --- Background.